### 2022-10-27 Draft_GFC.tex
version 27/10

@@

In order to have convergence when $m \to \infty$, one has to consider the normalise perimeter with the area of the window ($m^2$).

@@

@@

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{Variance_40.pdf}}
    \hspace{0.2cm}
 \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the values $b = 1$ and $C = 40$. }
\label{fig2}
\end{figure}

>>>>

the function $t \mapsto \mathbb{E}\left(f^{(i)}(t) \right)$ is even.

@@

In order to have convergence when $m$ goes to infinity, one has to consider the normalised perimeter with the area of the window ($m^2$).

@@

\textcolor{blue}{Decreasing behavior for all level $t$.}
 \text{if} \hspace{0.5cm} \tilde{\rho}(e_i) < \bar{\rho}(e_i) \hspace{0.5cm} \text{then} \hspace{0.5cm}\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \tilde{\rho}}(t)\right) > \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \bar{\rho}}(t)\right).
Let $x\in(-1,1)$ and $f: x \mapsto \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-x)}|N|}{\sqrt{2(1+x)}}\right)\right)$ we consider $a,b  \in (-1,1)$, such that $a > b$, 
f(a) - f(b) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) + \mathbb{E}\left(\Phi\left(\dfrac{2t - \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)- \Phi\left(\dfrac{2t - \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)\right) \\ 
= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{< 0} + \mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) \\
= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{< 0} + \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{<  0} \\
= \underbrace{\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right) - \Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right) + \mathbb{E}\left(\Phi\left(\dfrac{-2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)- \Phi\left(\dfrac{-2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)}_{<  0}
Thus if $a > b$
\mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-a)}|N|}{\sqrt{2(1+a)}}\right)\right) <  \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-b)}|N|}{\sqrt{2(1+b)}}\right)\right)

@@

\begin{figure}[H]
  \centering
    {\includegraphics[scale=0.3]{Variance_40_30_10_1.pdf}}
    \hspace{0.2cm}
 \caption{We represent of the values of $\mathbb{V}\left(\mathcal{P}\right)(t)$, the value of the theoretical curve Equation \eqref{Thisthofour} in (blue) and the empirical values are in orange, the computations were done with a Montecarlo $= 100000$ to compute the theoretical value and Montecarlo $= 2000$ to compute the empirical one, for the values $b = 1$ and $C = 40$. }
\label{fig2}
\end{figure}
